---
title: "VVN_TITLE"
author: "VVN_AUTHOR"
date: today
format:
  html:
    theme: [cosmo, styles.scss]
    toc: true
    toc-depth: 3
    toc-location: right
    toc-title: "Contents"
    embed-resources: true
    fig-width: 8
    fig-height: 5
    fig-dpi: 150
    smooth-scroll: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| include: false
library(vvnthemes)
library(knitr)
library(gt)
library(dplyr)
library(readr)

set_vvn_defaults()

# Load your processed data (needed for the summary table)
# df <- read_csv("data/processed/my_data.csv", show_col_types = FALSE)
```

::: {.hero}
## VVN_TITLE

::: {.hero-subtitle}
Visualizing Virginia's Numbers · Virginia Tech · `r format(Sys.Date(), "%Y")`
:::

[One sentence describing what this story is about and who it covers.]
:::

---

## Overview

> **Key Finding:** [State your single most important result here. **Bold the key number.** Keep it to 1–2 sentences.]

[2–3 sentences summarizing what you found and why it matters. Mention which figures support the finding and cite the data source.]

---

## Background

**Why this matters.** [Describe the policy or research context:]

- [What problem or question does this story address?]
- [Who is affected, and how?]
- [What data gap or opportunity does this analysis address?]

**Audience.** [Name the intended readers — e.g., policymakers, advocates, community organizations — and the issue area.]

---

## Data & Methods

| Item | Details |
|------|---------|
| **Source** | [Dataset name, organization, year] |
| **Geography** | [e.g., Virginia counties / independent cities] |
| **Period** | [e.g., 2018–2023] |
| **Variable** | [Description of the key variable(s) you are measuring] |

::: {.callout-note}
**Data note:** [Note any caveats — missing data, model-based estimates, comparability issues across years, or pandemic-related disruptions.]
:::

---

## Findings

### [Section title — e.g., Statewide Trend]

[1–2 sentences introducing Figure 1. Point out what the reader should notice and reference a specific number from the chart.]

```{r fig-01}
#| fig-cap: "[Caption: what the figure shows and the data source.]"
#| fig-alt: "[Alt text: chart type, key pattern, range of values — for screen readers.]"
# Replace 01_[name].png with your actual filename (e.g. 01_trend_statewide.png)
f <- "figures/01_[name].png"
if (file.exists(f)) knitr::include_graphics(f)
```

### [Section title — e.g., Trends by Group]

[1–2 sentences introducing Figure 2. Highlight the most important comparison or pattern.]

```{r fig-02}
#| fig-cap: "[Caption for Figure 2.]"
#| fig-alt: "[Alt text for Figure 2.]"
# Replace 02_[name].png with your actual filename
f <- "figures/02_[name].png"
if (file.exists(f)) knitr::include_graphics(f)
```

::: {.callout-important}
**Key observation:** [One sentence stating the most striking finding from Figure 2 — a gap, a reversal, an outlier.]
:::

### [Section title — e.g., Latest-Year Comparison]

[1–2 sentences introducing Figure 3 and pointing out the key comparison.]

```{r fig-03}
#| fig-cap: "[Caption for Figure 3.]"
#| fig-alt: "[Alt text for Figure 3.]"
# Replace 03_[name].png with your actual filename
f <- "figures/03_[name].png"
if (file.exists(f)) knitr::include_graphics(f)
```

### [Section title — e.g., Relationship Between Two Variables]

[1–2 sentences introducing Figure 4. Explain what the two axes represent and what the pattern means.]

```{r fig-04}
#| fig-cap: "[Caption for Figure 4.]"
#| fig-alt: "[Alt text for Figure 4.]"
# Replace 04_[name].png with your actual filename
f <- "figures/04_[name].png"
if (file.exists(f)) knitr::include_graphics(f)
```

### [Section title — e.g., County or Group Rankings]

[1–2 sentences introducing Figure 5. Note the range from lowest to highest and any notable entries.]

```{r fig-05}
#| fig-cap: "[Caption for Figure 5.]"
#| fig-alt: "[Alt text for Figure 5.]"
# Replace 05_[name].png with your actual filename
f <- "figures/05_[name].png"
if (file.exists(f)) knitr::include_graphics(f)
```

---

## Summary Table

```{r tbl-summary}
#| tbl-cap: "[Caption for the summary table.]"

# Replace with your own summary. Example:
#
# df |>
#   filter(year == max(year)) |>
#   group_by(`[Group]` = group_col) |>
#   summarise(
#     `[Column 1]` = round(mean(value_1), 1),
#     `[Column 2]` = round(mean(value_2), 1),
#     .groups = "drop"
#   ) |>
#   arrange(desc(`[Column 1]`)) |>
#   gt() |>
#   vvn_table(
#     title       = "[Table title]",
#     source_note = "Source: [Dataset] · VVN Analysis"
#   )
```

---

## Discussion

**Interpretation of findings:**

1. **[Finding 1 title].** [Describe and interpret the first major result — what does the pattern mean, not just what it shows?]
2. **[Finding 2 title].** [Connect the pattern to known context, prior research, or policy history.]
3. **Equity implications.** [Who benefits from current trends? Who is left behind, and why does that matter?]

**Limitations:**

- [Data availability or lag]
- [Geographic resolution — e.g., county-level data may mask sub-county variation]
- [Causal claims — note that the analysis is descriptive unless stated otherwise]

---

## Conclusion

[2–3 sentences summarizing the main takeaway.] These findings suggest that [policy implication]. Future work should examine [next research question].

::: {.callout-tip}
**For more:** Contact VVN at [vvn@vt.edu](mailto:vvn@vt.edu) or visit
[vvn.vt.edu](https://vvn.vt.edu).
:::

---

*Produced by Visualizing Virginia's Numbers · Virginia Tech*
*Built with [vvnthemes](https://github.com/yujuangao/VVN)*
