---
title: "VVN_TITLE"
author: "VVN_AUTHOR"
date: today
format:
  html:
    theme: [cosmo, styles.scss]
    toc: true
    toc-depth: 3
    toc-location: right
    toc-title: "Contents"
    embed-resources: true
    fig-width: 8
    fig-height: 5
    fig-dpi: 150
    code-fold: true
    code-summary: "Show code"
    smooth-scroll: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| include: false
library(vvnthemes)
library(ggplot2)
library(dplyr)

# Apply VVN defaults to all charts in this document
set_vvn_defaults()

# ── Load your data ──────────────────────────────────────────────────────────
# Replace with your actual data:
# df <- readr::read_csv("data/processed/my_data.csv")

set.seed(42)
df <- data.frame(
  year   = rep(2018:2023, each = 5),
  region = rep(c("Rural", "Small City", "Suburban",
                  "Urban Fringe", "Urban Core"), 6),
  value  = c(
    46, 50, 54, 58, 63,
    47, 51, 55, 59, 64,
    49, 53, 57, 61, 66,
    50, 54, 58, 63, 67,
    51, 56, 60, 64, 69,
    52, 57, 62, 66, 71
  ) + rnorm(30, 0, 0.5)
)
```

::: {.hero}
## VVN_TITLE

::: {.hero-subtitle}
Virginia Visualization Network · Virginia Tech · `r format(Sys.Date(), "%Y")`
:::

A data-driven look at [your topic] across Virginia communities.
:::

---

## Overview

> **Key Finding:** Rural Virginia counties have experienced a **12% increase**
> in [metric] between 2018 and 2023, narrowing the gap with urban areas for
> the first time in a decade.

This story examines [topic] across Virginia's diverse regional contexts.
We find that [summary of main result], with meaningful variation across
[geography / demographic group]. Our analysis draws on data from [source].

---

## Background

**Why this matters.** Describe the policy or research context:

- What problem or question does this story address?
- Who is affected, and how?
- What data gap does this analysis fill?

**Audience.** Policymakers, advocates, and community organizations working
on [issue area] in Virginia.

---

## Data & Methods

| Item | Details |
|------|---------|
| **Source** | [Dataset name, organization, year] |
| **Geography** | Virginia counties / [other unit] |
| **Period** | 2018–2023 |
| **Variable** | [Description of key variable] |

::: {.callout-note}
**Data note:** [Any caveats, missing data, or comparability issues.]
:::

```{r load-data}
#| include: false
# Data already loaded in setup chunk above.
```

---

## Findings

### Regional Trends Over Time

```{r fig-trend}
#| fig-cap: "Annual trends by region type, 2018–2023. Source: [Dataset]."
#| fig-alt: "Line chart showing value trends for five Virginia region types."

ggplot(df, aes(x = year, y = value, color = region, group = region)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 2.5) +
  scale_color_vvn("main") +
  labs(
    title    = "Regional Trends, 2018–2023",
    subtitle = "Virginia Visualization Network",
    x        = "Year",
    y        = "Value",
    color    = "Region"
  ) +
  vvn_source("[Dataset name]") +
  scatter_grid()
```

::: {.callout-important}
**Key observation:** Rural areas (maroon) show the steepest growth trajectory,
while urban cores (lighter shades) remain significantly higher in absolute terms.
:::

### Regional Comparison — Latest Year

```{r fig-bar}
#| fig-cap: "2023 values by region. Rural highlighted in orange."
#| fig-alt: "Horizontal bar chart comparing 2023 values across five region types."

df |>
  filter(year == max(year)) |>
  mutate(region = reorder(region, value),
         highlight = region == "Rural") |>
  ggplot(aes(x = value, y = region, fill = highlight)) +
  geom_col(width = 0.65) +
  geom_text(aes(label = round(value, 1)), hjust = -0.2, size = 3.5,
            color = "#3D3D3D") +
  scale_fill_manual(values = c(`TRUE` = "#E5751F", `FALSE` = "#861F41"),
                    guide  = "none") +
  scale_x_continuous(expand = expansion(mult = c(0, .15))) +
  labs(title    = paste("Regional Comparison ·", max(df$year)),
       subtitle = "Rural highlighted in orange",
       x = "Value", y = NULL) +
  vvn_source("[Dataset name]") +
  remove_ticks()
```

### Distribution of Values

```{r fig-hist}
#| fig-cap: "Distribution of values across all county-year observations."
#| fig-width: 6
#| fig-height: 3.5

ggplot(df, aes(x = value)) +
  geom_histogram(bins = 20, fill = "#861F41", color = "#FFFFFF", alpha = 0.9) +
  geom_vline(xintercept = mean(df$value), color = "#E5751F",
             linewidth = 1.2, linetype = "dashed") +
  annotate("text", x = mean(df$value) + 0.8, y = Inf,
           label = paste0("Mean: ", round(mean(df$value), 1)),
           color = "#E5751F", hjust = 0, vjust = 1.5, size = 3.5) +
  labs(title = "Value Distribution",
       x = "Value", y = "Count") +
  vvn_source("[Dataset name]")
```

### County Map

```{r map}
#| fig-cap: "County-level map. Replace with your spatial data."

# Uncomment and replace with your county-level sf data:
# library(leaflet)
# leaflet(va_counties) |>
#   vvn_map_style(
#     data      = va_counties,
#     value_col = "your_variable",
#     title     = "Your Variable"
#   )

# Placeholder:
ggplot(df |> filter(year == max(year)),
       aes(x = reorder(region, value), y = value, fill = value)) +
  geom_col() +
  scale_fill_vvn_c("maroon_seq") +
  coord_flip() +
  labs(title    = "[ Replace with county map ]",
       subtitle = "Add leaflet + vvn_map_style() for an interactive choropleth",
       x = NULL, y = "Value", fill = "Value") +
  vvn_source("Placeholder")
```

---

## Summary Table

```{r tbl-summary}
#| tbl-cap: "Summary statistics by region, 2018–2023."

summary_df <- df |>
  group_by(Region = region) |>
  summarise(
    `Mean`          = round(mean(value), 1),
    `2023 Value`    = round(value[year == max(year)], 1),
    `Change (pts)`  = round(value[year == max(year)] - value[year == min(year)], 1),
    .groups = "drop"
  ) |>
  arrange(desc(`2023 Value`))

# With gt (recommended):
# library(gt)
# gt(summary_df) |>
#   vvn_table(title       = "Regional Summary Statistics",
#              source_note = "Source: [Dataset] · VVN Analysis")

# Fallback to knitr::kable:
knitr::kable(summary_df, align = c("l", "r", "r", "r"))
```

*Source: [Dataset] · VVN Analysis*

---

## Discussion

**Interpretation of findings:**

1. **Finding 1.** Describe and interpret the first major result.
2. **Finding 2.** Connect the pattern to known context or prior research.
3. **Equity implications.** Who benefits or is left behind?

**Limitations:**

- Data availability: [any gaps]
- Geographic resolution: [county vs. sub-county]
- Causal claims: [note that analysis is descriptive unless otherwise stated]

---

## Conclusion

[2–3 sentences summarizing the main takeaway.] These findings suggest that
[policy implication]. Future work should examine [next research question].

::: {.callout-tip}
**For more:** Contact VVN at [vvn@vt.edu](mailto:vvn@vt.edu) or visit
[vvn.vt.edu](https://vvn.vt.edu).
:::

---

*Produced by the Virginia Visualization Network · Virginia Tech*
*Built with [vvnthemes](https://github.com/vt-vvn/vvnthemes)*
