---
title: "VVN_TITLE"
subtitle: "VVN_SUBTITLE"
author: "VVN_AUTHOR"
date: today
format:
  html:
    theme: [cosmo, styles.scss]
    toc: true
    toc-depth: 2
    toc-location: left
    number-sections: true
    smooth-scroll: true
    code-fold: true
    code-tools: true
    fig-width: 8
    fig-height: 4.5
    fig-dpi: 150
    embed-resources: true
    link-external-icon: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| include: false
library(vvnthemes)
library(ggplot2)
library(knitr)
library(dplyr)

set_vvn_defaults()
```

::: {.vvn-header}
::: {.vvn-rubric}
Insights · Visualizing Virginia's Numbers · Virginia Tech
:::

::: {.vvn-topics}
[Topic 1]{.vvn-tag}
[Topic 2]{.vvn-tag}
[Topic 3]{.vvn-tag}
:::

## VVN_TITLE {.unnumbered .unlisted}

::: {.vvn-subtitle}
VVN_SUBTITLE
:::

::: {.vvn-byline}
By **VVN_AUTHOR** · Visualizing Virginia's Numbers (VVN) · Virginia Tech · VVN_DATE
:::
:::

[2–3 sentences introducing the story: what question it answers, which data it uses, and why it matters for Virginia communities.]

::: {.vvn-stats-row}
::: {.vvn-stat}
[##]{.big-number}
[Stat 1 label]{.stat-label}
:::

::: {.vvn-stat}
[##]{.big-number}
[Stat 2 label]{.stat-label}
:::

::: {.vvn-stat}
[##]{.big-number}
[Stat 3 label]{.stat-label}
:::
:::

<details class="about-research">
<summary>About This Research</summary>
<div class="about-content">

### Background

[Describe the policy or research context — what problem this analysis addresses, who is affected, and why it matters.]

### Data & Methods

| Item | Details |
|------|---------|
| **Source** | [Dataset name, organization, year] |
| **Geography** | [e.g., Virginia counties / independent cities] |
| **Period** | [e.g., 2018–2023] |
| **Variable** | [Key variable(s) being measured] |

### Limitations

- [Data availability or lag]
- [Geographic resolution caveats]
- [Causal claims — note that the analysis is descriptive unless stated otherwise]

</div>
</details>

---

## Finding 1 Title {.finding}

::: {.finding-statement}
[Write the main finding as a bold headline statement — one sentence summarizing what the data shows.]
:::

[1–2 paragraphs explaining this finding. Reference the figure below and highlight the key number or pattern the reader should notice.]

<!-- OPTION A: Static figure (from scripts/analysis.R → figures/) -->
```{r fig-01}
#| fig-cap: "[Caption: what the figure shows and the data source.]"
#| fig-alt: "[Alt text: chart type, key pattern, range of values.]"
f <- "figures/01_[name].png"
if (file.exists(f)) knitr::include_graphics(f)
```

<!-- OPTION B: Interactive HTML map/widget (from assets/) -->
<!-- Uncomment the block below and remove the R chunk above if using an interactive HTML file. -->
<!-- Place your .html file in assets/ and update the src path and title. -->
<!--
::: {.map-card}
<iframe src="assets/[map_name].html" height="580" style="width:100%;border:none;" title="[Map title]"></iframe>
::: {.map-caption}
**Figure 1.** [Caption describing the interactive map.]
[Source: [Dataset name]]{.vvn-source}
:::
:::
-->

---

## Finding 2 Title {.finding}

::: {.finding-statement}
[Second major finding as a headline statement.]
:::

[1–2 paragraphs explaining this finding.]

```{r fig-02}
#| fig-cap: "[Caption for Figure 2.]"
#| fig-alt: "[Alt text for Figure 2.]"
f <- "figures/02_[name].png"
if (file.exists(f)) knitr::include_graphics(f)
```

---

## Finding 3 Title {.finding}

::: {.finding-statement}
[Third major finding as a headline statement.]
:::

[1–2 paragraphs explaining this finding.]

```{r fig-03}
#| fig-cap: "[Caption for Figure 3.]"
#| fig-alt: "[Alt text for Figure 3.]"
f <- "figures/03_[name].png"
if (file.exists(f)) knitr::include_graphics(f)
```

---

## Conclusion {.unnumbered}

[2–3 sentences summarizing the main takeaway.] These findings suggest that [policy implication]. Future work should examine [next research question].

---

*Produced by Visualizing Virginia's Numbers · Virginia Tech*
*Built with [vvnthemes](https://github.com/yujuangao/VVN)*
